\cvsection{Education}
\begin{cventries}
  \cventry
    {Master Degree in Aerospace Engineering}
    {Universidade Técnica de Lisboa - Instituto Superior Técnico (IST)}
    {Lisboa, Portugal}
    {Sep. 2006 - Jul. 2013}
    {
      \begin{cvitems}
        \item {Master thesis, Computational Model for a Helicopter Main Rotor with Men-on-the-Loop, Computer Simulation, C++, Visual Studio for Real Time Application. 
This master thesis achieved a connection between industry and university. Using state of the art computational power and simple aerodynamic models, it was created flight model input data for a Helicopter Simulator System.
}
      \end{cvitems}
    }
    
    \cventry
    {Alten Training}
    {Effective and Efficient Communication Course}
    {Breda, Netherlands}
    {Feb. 2018}
    {  \begin{cvitems}
        \item Course on how to improve Effective and Efficient Communication with customers and work colleges.
        \end{cvitems}
  }
  
    \cventry
    {Alten Training}
    {Alige Course}
    {Rotherdam, Netherlands}
    {Jun. 2017}
    {  \begin{cvitems}
        \item Agile General Course
        \item Scrum Master
        \end{cvitems}
  }
  
   \cventry
    {}
    {Extracurricular Activities}
    {Lisbon, Portugal}
    {Sep. 2006 - Jul. 2013}
    {
      \begin{cvitems}
    \item {HABalua - Design and Construction of a controllable High Altitude Atmospheric Balloon.}
    \item {Projecto Shell Eco-Marathon at IST - Founding member (While Studying) Design and Build the 1st Portuguese Fuel Cell Powered Electric vehicle to participate in the international competition Shell Eco-Marathon. 23rd place out of 200 teams achieved on the 2009 race edition.} 
      \end{cvitems}
    }
\end{cventries}

